Topology of the $O(3)$ non-linear sigma model under the gradient flow

### 2021-10-07 proceedings/draft.tex
add proceeding template

\section{...}

>>>>

\section{The Non-Linear Sigma Model}
            We study the $O(3)$ non-linear sigma model (NLSM) in 1+1 dimensions, defined by the Euclidean action
            \begin{equation*}
                \label{eq:nlsm euclidean action}
                S_E = \frac{\beta}{2} \int d^2x \; \left[ \left(\partial_t \e\, \right)^2+ \left( \partial_x \e\,\right)^2 \right]
            \end{equation*}
        where, $\e$ is 3-component real vector constrained by $|\e\,|=1$ and $\beta$ is the inverse coupling constant. In solid-state systems, this model describes Heisenberg ferromagnets \cite{callan1985} and in nuclear physics, it acts as a prototype for quantum chromodynamics (QCD), the gauge theory that describes the strong nuclear force. In general, the NLSM shares key features with non-Abelian gauge theories such as QCD, including a mass gap and asymptotic freedom \cite{polyakov1975}. Therefore, the NLSM is a useful model for exploring the effect of these properties in a simpler system.

            %\item Prototypical model for strong nuclear force
                    %\item Models Heisenberg ferromagnets
                    %\item Applications to string theory
                %\end{itemize}
            %\item<4-> Merits
                %\begin{itemize}
                    %\item mass gap
                    %\item asymptotic freedom
                %\end{itemize}
        \end{itemize}
